### 2019-07-11 2-Chapters/Conclusion/conclusion.tex
Okay, fixed bug of transparent last page

Moreover, from a theoretical aspect, even though it was found hard to propose a rigorous analysis of our model of IoT networks, because of the large number of devices having different random and unpredictable activation patterns, our contributions also include an analysis of two restricted models.
%
On the one hand, we considered a model where the devices have data to transmit at each time step, relaxing the hypothesis of a random activation process (with a small probability, as IoT devices have low duty cycles), and thus by restricting to the case of at most $M \leq K$ devices using a wireless standard with $K$ orthogonal frequency channels.
This first model is similar to the multi-player bandit model studied in the last $10$ years, and for stationary and stochastic environments we were able to propose a state-of-the-art algorithm, \MCTopM.
Our proposed algorithm performs very well in practice and obtains interesting guarantees on its regret, as well as on the number of radio collisions and on radio reconfigurations that the devices will suffer if they all implement our solution.
%
On the other hand, we studied a model that focuses on only one device but relaxes the hypothesis of stationarity on the surrounding radio traffic, and considers that is can be stationary in consecutive intervals of time, of unknown durations. This second model is similar to the piece-wise stationary (or abruptly-changing) bandit model studied since the $2000$s, and we solved it by proposing a new actively adaptive bandit policy, for which we obtained state-of-the-art results, in terms of its regret and its false alarm probability and delay of detection.

@@

% % As discussed at the end of each chapter,
% % All the models, simulations,
% What we presented above in each chapter suggest the following directions of future studies.

@@

% ----------------------------------------------------------------------------
% \subsection*{Other directions of future works}
\subsection*{Unifying multi-player and non-stationary bandits.}
%
%
Finally, another interesting direction of future work is to study non-stationary distributed multi-players bandits, to unify the models from Chapter~\ref{chapter:5} and~\ref{chapter:6}.
A natural extension of the non-stationary model is to consider non-communicating players cooperating in a decentralized way to play the same bandit game, as it was proposed recently in \cite{WeiSrivastava18Distributed}.
%
We could also build on the proof technique used in this paper, even if we are interested in removing the hypothesis that player $j$ knows its ID $j\in[M]$ before starting to play.
%
A promising direction is to directly try to join our contributions from Chapter~\ref{chapter:5} and~\ref{chapter:6}, and propose an efficient algorithm using three parts:
\klUCB{} indexes for arm selection,
\MCTopM{} for orthogonalization (\ie, dealing with collisions),
and the Bernoulli GLR break-point detector for non-stationarity (\ie, dealing with abrupt changes).
The three parts should be inter-connected, the same way we built \MCTopM-\klUCB{} and \GLRklUCB, by connecting two of the three components together.
We propose a simple idea to incorporate the detected change-points by B-\GLR{} test in the orthogonalization procedure \MCTopM: whenever a change-point is detected, the player is no longer ``fixed'' on its chosen arm.
%
Even if preliminary numerical simulations showed promising results,
analyzing this strategy that combine \MCTopM, \GLR{} and \klUCB{} is left as a challenging future work.

@@

Another question of highest interest is to look for a unique ``unified'' algorithm that can be used in all the different settings studied in this thesis, and maybe others, and automatically adapt to the setting at hand.
For instance, even if \GLRklUCB{} is very efficient for piece-wise stationary problems, its forced exploration makes it sub-optimal for stationary problems.
Another example is for multi-players bandits, where \MCTopM-\klUCB{} performs sub-optimally on piece-wise stationary problems.
% if we consider the proposed extension of \MCTopM-\klUCB{} that estimates the number $M$ of players, i
One approach to obtain a unified ``master'' algorithm could be to use expert aggregation on the different state-of-the-art algorithms presented in this thesis, and as each one was proven to be efficient in one setting, the resulting aggregated algorithm would also be efficient in each of the different settings.
As this approach does not seem theoretically promising, as illustrated in Section~\ref{sec:25:theory},
a preferred approach could be to design a ``unified'' algorithm which adapts automatically to the kind of problem it is facing.

@@

\begin{center}
    Je vous remercie d'avoir lu cette thèse. Merci de me signaler toute erreur par courriel :
    \\
    Thanks for reading this document. Please notify me about any mistake by e-mail:\\
    \href{https://github.com/Naereen/phd-thesis/issues/new}{\texttt{Lilian.Besson}\texttt{@}\texttt{Crans.org}}
\end{center}

% \hr{}

@@

\begin{small}
\begin{quote}
    \emph{-- Les rêves, ça se compare pas\ldots}\\
    Alexandre Astier, \emph{Kaamelott}, Livre VI, Épisode 9, ``Dies Irae''.
    %  écrit par Alexandre Astier.
\end{quote}
\end{small}

>>>>

Moreover, from a theoretical aspect, even though it was found hard to propose a rigorous analysis of our model of IoT networks, because of the large number of devices having different random and unpredictable activation patterns, our contributions also include an analysis of two restricted models.
%
On the one hand, we considered a model where the devices have data to transmit at each time step, relaxing the hypothesis of a random activation process (with a small probability, as IoT devices have low duty cycles), and thus by restricting to the case of at most $M \leq K$ devices using a wireless standard with $K$ orthogonal frequency channels.
This first model is similar to the multi-player bandit model studied in the last $10$ years, and for stationary and stochastic environments we were able to propose an efficient algorithm, \MCTopM.
Our proposed algorithm performs very well in practice and we obtained interesting guarantees on its regret, as well as on the number of radio collisions and on radio reconfigurations that the devices will suffer if they all implement our solution.
%
On the other hand, we studied a model that focuses on only one device but relaxes the hypothesis of stationarity on the surrounding radio traffic, and considers that is can be stationary in consecutive intervals of time, of unknown durations. This second model is similar to the piece-wise stationary (or abruptly-changing) bandit model studied since the $2000$s, and we solved it by proposing a new actively adaptive bandit policy, for which we obtained state-of-the-art results, in terms of its regret and its false alarm probability and delay of detection.

@@

% % As discussed at the end of each chapter,
% % All the models, simulations,
The works presented in each chapter suggest possible directions of future studies.

@@

% ----------------------------------------------------------------------------
% \subsection*{Other directions of future works}
\subsection*{Unifying multi-player and non-stationary bandits.}
%
%
A natural next step after this thesis is to study non-stationary distributed multi-players bandits, to unify the models from Chapter~\ref{chapter:5} and~\ref{chapter:6}.
A natural extension of the non-stationary model is to consider non-communicating players cooperating in a decentralized way to play the same bandit game, as it was proposed recently in \cite{WeiSrivastava18Distributed}.
%
We could also build on the proof technique used in this paper, even if we are interested in removing the hypothesis that player $j$ knows its ID $j\in[M]$ before starting to play.
%
A promising direction is to directly try to join our contributions from Chapter~\ref{chapter:5} and~\ref{chapter:6}, and propose an efficient algorithm using three parts:
\klUCB{} indexes for arm selection,
\MCTopM{} for orthogonalization (\ie, dealing with collisions),
and the Bernoulli GLR break-point detector for non-stationarity (\ie, dealing with abrupt changes).
The three parts should be inter-connected, the same way we built \MCTopM-\klUCB{} and \GLRklUCB, by connecting two of the three components together.
We propose a simple idea to incorporate the detected change-points by B-\GLR{} test in the orthogonalization procedure \MCTopM: whenever a change-point is detected, the player is no longer ``fixed'' on its chosen arm.
%
Even if we already obtained promising results on preliminary numerical simulations,
analyzing such a strategy that combines \MCTopM, \GLR{} and \klUCB{} is left as a challenging future work.

@@

% Another question of highest interest is to look for 
Finally, I would be very interested in looking at a unique ``unified'' algorithm that can be used in all the different settings studied in this thesis, and maybe others, and automatically adapt to the setting at hand.
For instance, even if \GLRklUCB{} is very efficient for piece-wise stationary problems, its forced exploration makes it sub-optimal for stationary problems.
Another example is for multi-players bandits, where \MCTopM-\klUCB{} performs sub-optimally on piece-wise stationary problems.
% if we consider the proposed extension of \MCTopM-\klUCB{} that estimates the number $M$ of players, i
One approach to obtain a unified ``master'' algorithm could be to use expert aggregation on the different state-of-the-art algorithms presented in this thesis, and as each one was proven to be efficient in one setting, the resulting aggregated algorithm would also be efficient in each of the different settings.
As this approach does not seem theoretically promising, as illustrated in Section~\ref{sec:25:theory},
a preferred approach could be to design a ``unified'' algorithm which adapts automatically to the kind of problem it is facing.

@@

\begin{small}
\begin{center}
    Je vous remercie d'avoir lu cette thèse. Merci de me signaler toute erreur par courriel ou sur GitHub :
    \\
    Thanks for reading this document. Please notify me about any mistake by e-mail or on GitHub:\\
    $\hookrightarrow$ \href{https://github.com/Naereen/phd-thesis/issues/new}{\texttt{GitHub.com/Naereen/phd-thesis/issues/new}}\\
    $\hookrightarrow$ \href{mailto:Lilian.Besson_at_Crans.org}{\texttt{Lilian.Besson}\texttt{@}$\{$\texttt{Crans.org},\texttt{Inria.fr},\texttt{live.fr}$\}$}
\end{center}
\end{small}

% \vfill{}

@@

\begin{small}
\begin{quote}
    \emph{-- Les rêves, ça se compare pas\ldots}
    Alexandre Astier, \emph{Kaamelott}, Livre VI, Épisode 9, ``Dies Irae''.
    %  écrit par Alexandre Astier.
\end{quote}
\end{small}
